% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{multicol}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
  {\setlength{\leftmargin}{#1}}%
  \item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
  {\setlength{\leftmargin}{-0.5#1}}%
  \item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
  #1 &
  #2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Zachary Forman}}

51 Kintore Avenue\ \ \textbullet
\ \ Prospect\ 5082\ \ \textbullet
\ \ Adelaide, South Australia
\\
+61 466 020 412\ \ \textbullet
\ \ au.zachary.forman@gmail.com
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Work Experience}

\begin{itemize}
  \parskip=0.1em

  \item
  \headerrow
    {\textbf{Google Sydney}}
    {\textbf{Chrome}}
  \\
  \headerrow
    {\emph{Software Engineering Intern}}
    {\emph{November 2015 -- February 2016}}
  \begin{itemize*}
    \item Improved determinism of Chrome build process significantly, reducing
          the number of non-deterministic outputs on Linux by tens of thousands.
    \item Designed and implemented an experimental framework in javascript
          for learning about the Chrome build.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Google Sydney}}
    {\textbf{Drive}}
  \\
  \headerrow
    {\emph{Software Engineering Intern}}
    {\emph{November 2014 -- February 2015}}
  \begin{itemize*}
    \item Designed and implemented an Android application.
    \item Adapted a pretrained neural network for recognition of a subset of
          images, with ~94\% accuracy.
    \item Worked independently, producing $> 5000$ lines of high quality code.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Computer Science}}
    {\textbf{Adelaide University}}
  \\
  \headerrow
    {\emph{Casual Teaching}}
    {\emph{August 2014 -- present}}
  \begin{itemize*}
    \item Taught first year students fundamentals of Computer Science and
          programming.
    \item Ran practicals and workshops for first year courses.
    \item Took tutorials for a first year algorithms and data structures course.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{AutoID Labs}}
    {\textbf{Adelaide}}
  \\
  \headerrow
    {\emph{Summer Intern}}
    {\emph{December 2013 -- March 2014}}
  \begin{itemize*}
    \item Built and helped design a \CPP \ stream processor that interfaced with
          pre-existing middleware and machine learning algorithms to generate a
          stream of predictions.
    \item Built a visual C$^\sharp$ application to interface with RFID readers
          and provide a stream of tag reports.
    \item Reference: Dr. Damith Ranasinghe (damith.ranasinghe@adelaide.edu.au)
  \end{itemize*}

\end{itemize}

\subsection*{Leadership}

\begin{itemize}
  \parskip=0.1em

  \item
  {\textbf{President of Computer Science Club}}
  \\
  \headerrow
    {\emph{Adelaide University}}
    {\emph{November 2013 -- November 2015}}
  \begin{itemize*}
    \item Improved relationship with the Computer Science faculty, leading to
          increased involvement during O-week and a large recruitment of first
          year students.
    \item Promoted a healthier club environment, which contributed to a more
          diverse club than in past years.
    \item Encouraged a culture of excellence within the club, which contributed
          to a significant number of club members (5+) getting internships at
          leading tech companies, including Google and Microsoft.
  \end{itemize*}

  \item
  {\textbf{Peer Mentor}}
  \\
  \headerrow
    {\emph{Adelaide University}}
    {\emph{2014 -- Present}}
  \begin{itemize*}
    \item Assisting new students in transitioning to University.
    \item Running introductory tours and lectures for incoming students.
    \item Outreach events to high schools.
  \end{itemize*}

\end{itemize}

\subsection*{Core Technical Skills}

\begin{indentsection}{\parindent}
\begin{multicols}{2}
\hyphenpenalty=1000
  \headerrow {\textbf{Language}} {\textbf{Years Experience}}\\
  \headerrow {\CPP} {3.5}\\
  \headerrow {C} {3}\\
  \headerrow {Java} {2.5}\\
  \headerrow {Go} {0.5}\\
  \headerrow {Python} {0.75}\\


  \headerrow {\textbf{Technology}} {\textbf{Years Experience}}\\
  \headerrow {SVN} {4}\\
  \headerrow {Regular Expressions} {3}\\
  \headerrow {\LaTeX} {3}\\
  \headerrow {Git} {2}\\
  \headerrow {Android} {0.5}\\
\end{multicols}
\end{indentsection}

\newpage

\subsection*{Education}

\begin{itemize}
  \parskip=0.1em

  \item
  {\textbf{Adelaide University}}
  \\
  \headerrow
    {\emph{Bachelor of Engineering (Honours) (Software Engineering)}}
    {\emph{2013 -- Present}}
  \\
  Expected Graduation: November 2016
  \begin{itemize*}
    \item GPA: 6.6/7.0
    \item Selected key courses:
    \begin{itemize*}
      \item \headerrow
        {Object Oriented Programming (2013 s1)}
        {High Distinction}
      \item \headerrow
        {Algorithm Design and Data Structures (2013 s2)}
        {High Distinction}
      \item \headerrow
        {Systems Programming in C and C++ (2013 s2)}
        {High Distinction}
      \item \headerrow
        {Computer Networks and Applications (2014 s1)}
        {High Distinction}
      \item \headerrow
        {Artificial Intelligence (2014 s1)}
        {High Distinction}
      \item \headerrow
        {Operating Systems (2014 s2)}
        {High Distinction}
      \item \headerrow
        {Event Driven Computing (2014 s2)}
        {High Distinction}
      \item \headerrow
        {Computer Vision (2015 s1)}
        {Distinction}
      \item \headerrow
        {Distributed Systems (2015 s2)}
        {Distinction}
      \item \headerrow
        {Evolutionary Computation (2015 s2)}
        {High Distinction}
      \item \headerrow
        {Introduction to Statistical Machine Learning (2015 s2)}
        {High Distinction}
      \item \headerrow
        {Distributed Databases and Data Mining (2016 s1)}
        {Pending}
      \item \headerrow
        {Mining Big Data (2016 s2)}
        {Pending}
    \end{itemize*}
    \item Recipient of Adelaide University Undergraduate Scholarship for outstanding academic merit.
  \end{itemize*}

\end{itemize}

\subsection*{Miscellaneous}
\begin{itemize}
  \item Competitions
    \begin{itemize}
      \item Google Code Jam 2013-2015 (Qualified)
      \item ACM 2015 (2nd place on site)
      \item ACM 2014 (3rd place on site)
      \item ACM 2013
    \end{itemize}
  \item
  \headerrow
    {Github \& Personal Projects}
    {\url{https://www.github.com/ZacharyForman}}
    \begin{itemize}
      \item \href{https://github.com/ZacharyForman/Binary_Matcher}{Binary Matcher}
        \begin{itemize}
          \item Tool for analyzing binaries, and potentially doing clever
                binary diffing.
          \item Learned about ELF file format and how binaries are run on Linux.
        \end{itemize}
      \item \href{https://github.com/ZacharyForman/net}{net}
        \begin{itemize}
          \item C++ wrapper of BSD sockets, and several other utilities for
                code that interacts with the Internet
          \item Learned more about BSD sockets, and experimented with API
                design.
        \end{itemize}
      \item \href{https://github.com/ZacharyForman/cpu}{cpu}
        \begin{itemize}
          \item Instruction architecture simulator for the DLX architecture.
          \item Improved my C programming ability and consolidated my knowledge
                of DLX.
        \end{itemize}
    \end{itemize}
\end{itemize}


\end{document}
